How and Why to run a Hack Week

### 2017-09-19 sections/what.tex
Attempts to address comment made by BFG regarding hackathon criticsms.

We note that the terminology for these events is constantly evolving, and that the ``hackathon'' concept may have implicit connotations that are disfavored in some communities.
One criticism of hackathons is that they propel the ``geek'' stereotype and may present a barrier to creating an inclusive working environment, especially for individuals traditionally underrepresented in science and technology \cite{Decker2015}.
Another problem is the competitive atmosphere of many industry hackathons, where teams actively compete for prizes.
Because certain groups are more risk-averse than others, and risk-aversion traces demographics like gender, we urge caution when contemplating making an event competitive.

>>>>

We note that the terminology for these events is constantly evolving, and that the ``hackathon'' concept may have implicit connotations that are disfavored in some communities.
One criticism of hackathons is that they propel the ``geek'' stereotype and may present a barrier to creating an inclusive working environment, especially for individuals traditionally underrepresented in science and technology \cite{Decker2015}.
This criticism needs to be actively addressed both through participant selection (see below), and by addressing the possibility that some participants may experience an ``imposter syndrome'' within such circumstances \cite{clance1978imposter}.
Also, while many industry hackathons are competitive, with teams actively competing to solve the same problems for prizes that are awarded prizes, academic hackathons, and specifically the hack weeks that we have organized events are not explicitely competitive
